---
title: "Analysis France"
author: "Sebastian Sternberg"
date: "10 January 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





```{r}

rm(list = ls())

require(magrittr)
require(haven)
require(foreign)
require(dplyr)

library(tidyverse)


```

Read in the data from France:




Attention: Scale is reversed in France:

1	Tout à fait d’accord
2	Plutôt d’accord
3	Ni d’accord, ni pas d’accord
4	Plutôt pas d’accord
5	Pas d’accord du tout
97  Je ne sais pas
98  Je ne veux pas répondre

# Descriptives Trust (Figure 1)

```{r}

load("../Data/gip_merge.Rda")

#trust in gfc
prop.table(table(gip_merge$AK27031, useNA = "ifany")) #trust_bverfg


#create data set for the plot
trust_gfcc <- as.data.frame.table(prop.table(table(gip_merge$AK27031)), 
                                  row.names = c("no trust at all", "no trust", "rather not trust", "indifferent",
                                                "rather trust",
                                                "high trust", "very high trust"),
                                  responseName = "Percentage")
trust_gfcc$Var1 <- rownames(trust_gfcc)


#create data set for France:
library(haven)

enef <- read_dta("../Data/ENEF2017_legitimacy_experiment.dta")

enef$QCONF4_2[enef$QCONF4_2 > 11] <- NA

#has 10 point scale
table(enef$QCONF4_2, useNA = "ifany")

#recode: collapse the highest and lowest category

enef$QCONF4_2_fac <- as.factor(enef$QCONF4_2)

enef <- enef %>%
  mutate(trust_cc = recode(QCONF4_2_fac, 
                           "0" = "no trust at all",                                       
                           "1" = "no trust at all",
                           "2" = "no trust at all",
                           "3" = "no trust",
                           "4" = "rather not trust",
                           "5" = "indifferent",
                           "6" = "rather trust",
                           "7" = "high trust",
                           "8" = "very high trust",
                           "9" = "very high trust",
                           "10" = "very high trust"
  )
  )

#check coding:

table(enef$trust_cc, enef$QCONF4_2_fac)

#create data set for the plot
trust_cc <- as.data.frame.table(prop.table(table(enef$trust_cc)),
                                responseName = "Percentage")

require(ggplot2)
require(ggthemes)
require(plyr)

plot_data_trust <- rbind.data.frame(trust_gfcc, trust_cc)
plot_data_trust$country <- c(rep("Germany", 7), rep("France", 7))


#change percentage to 100 for plotting
plot_data_trust$Percentage <- plot_data_trust$Percentage*100

#correct the order of the factor such that it is correctly plotted
plot_data_trust$Var2 <-  factor(plot_data_trust$Var1 , levels = c(unique(plot_data_trust$Var1)))


plot_data_trust$country <- as.factor(plot_data_trust$country)


p <- ggplot(plot_data_trust, aes(x = fct_rev(country), y = Percentage, fill = fct_rev(Var2))) +
  geom_bar(stat='identity',  width = .7, colour="black", lwd=0.1) + 
  scale_fill_manual(values=c("gray45", "gray55", "gray65", "gray75", "gray90", "gray95", "gray100")) +
  #scale_fill_grey(start=0.1, end=0.9) + 
  geom_text(#label= paste(round(plot_data_trust$Percentage, 0), "%", sep = ""), 
    label = round(plot_data_trust$Percentage, 0),
    position=position_stack(vjust=0.5), 
    color="black", size=5) +
  labs(y="Level of Trust (in %)", x="") + 
  guides(fill=guide_legend(""))+
  coord_flip()+
  theme_tufte()+
  theme(text = element_text(size=20))+
  theme(
    axis.text.x=element_blank(),
    axis.ticks.x=element_blank())


#save
outfolder <- ("../Figures")

pdf(paste(outfolder,"/comparison_trust.pdf",sep = ""), width = 12, height = 8)
p
dev.off()

```



```{r}


df <- read_dta("../Data/ENEF2017_legitimacy_experiment.dta")


table(df$QEXPPOSINS, useNA = "ifany") #experimental groups pension

table(df$PEXPPOSINS, useNA = "ifany") #experimental groups school 


#Recode experimental groups:

class(df$ID12)
class(df$QEXPPOSINS)


df$PEXPPOSINS <- as.factor(df$PEXPPOSINS)

#recode the education variable

df <- df %>%
  mutate(experiment_groups_school = recode(PEXPPOSINS, 
                                    "1" = "Control",                                       
                                    "2" = "CC_Approves",
                                    "3" = "CC_Disapproves",
                                    "4" = "Haut_Conseil_Edu_Approves",
                                    "5" = "Haut_Conseil_Edu_Disapproves"
  )
  )


df$QEXPPOSINS <- as.factor(df$QEXPPOSINS)

#recode the pension variable
df <- df %>%
  mutate(experiment_groups_pension = recode(QEXPPOSINS, 
                                    "1" = "Control",                                       
                                    "2" = "CC_Approves",
                                    "3" = "CC_Disapproves",
                                    "4" = "Conseil_d_Orientation_appr.",
                                    "5" = "Conseil_d_Orientation_disappr."
  )
  )


#recode NAs
df$PCCFAITH[df$PCCFAITH > 6] <- NA
df$QCCFAITH[df$QCCFAITH > 6] <- NA

table(df$PCCFAITH, useNA = "ifany")
table(df$QCCFAITH, useNA = "ifany")


#short check:

#first reverse to have the German coding:

df$PCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_school  = recode(PCCFAITH, 
                             "1" = "5",                                  
                             "2" = "4",
                             "3" = "3",
                             "4" = "2",
                             "5" = "1"
  )
  ) 
#order levels again

df$rating_school <- factor(df$rating_school, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_school, df$PCCFAITH)


###do the same for the pension variable

df$QCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_pension  = recode(QCCFAITH, 
                             "1" = "5",                                  
                             "2" = "4",
                             "3" = "3",
                             "4" = "2",
                             "5" = "1"
  )
  ) 
#order levels again

df$rating_pension <- factor(df$rating_pension, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_pension, df$QCCFAITH)


#################
#continue recoding: now to 3-point scale

df <- df %>%
  mutate(rating_school_factor = recode(rating_school, 
                             "1" = "disagree",                                  
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_school, df$rating_school_factor, useNA = "ifany")


#same for pension policy experiment

df <- df %>%
  mutate(rating_pension_factor = recode(rating_pension, 
                             "1" = "disagree",                                  
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_pension, df$rating_pension_factor, useNA = "ifany")

```


# Ordinal Probit School Security Law (Figure 2b France Results)

```{r}

library(MASS)

m_enef_school <- polr(rating_school_factor ~ experiment_groups_school, 
                   data = df, 
               method = "probit",
                   Hess=TRUE)

summary(m_enef_school)

#pvalues

(ctable <- coef(summary(m_enef_school)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))


#######################
###plot coefs:

# Extract coefficient estimates

coef_vec <- summary(m_enef_school)$coefficients[1:4,1] 
coef_vec <- c(coef_vec, "NA","NA") %>% as.numeric()


names_vec_nov <- c("CC \n Approves", 
                   "CC \n Disapproves", 
                   "Haut Conseil \n de l'Éducation \n Approves", 
                   "Haut Conseil \n de l'Éducation \n Disapproves", " ", " ") # Extract variable names

se_vec <- summary(m_enef_school )$coefficients[1:4,2]
se_vec <- c(se_vec, "NA", "NA") %>% as.numeric()


outfolder <- ("../Figures")

pdf(paste(outfolder,"/coefplot_enef_school.pdf",sep = ""), width = 8, height = 8)

#adjust margins:
par(mar  = c(4,7,2,2))

plot(coef_vec, 6:1, 
     pch=19, 
     cex=.8, 
     axes=F, 
     ylab="", 
     xlab="Ordered Probit Coefficients", 
     xlim=c(-0.4, 0.4))
axis(1)
axis(2, at=6:1, label=names_vec_nov, col="white", las = 1)
abline(v=0, lty=2) # add zero reference line

#plot 95% CIs
segments(coef_vec - qnorm(0.975)*se_vec,  6:1, coef_vec + qnorm(0.975)*se_vec, length(coef_vec):1) # add confidence intervals

#add 90% CIs
segments(coef_vec - qnorm(0.95)*se_vec,  6:1, coef_vec + qnorm(0.95)*se_vec, length(coef_vec):1, lwd = 2) # add confidence intervals

dev.off()



```

There is no effect of legitimization in the France case. However, the Haut Conseil has a legitimizing effect in case of an approval.

Make the corresponding regression table for the Appendix:

```{r}
library(stargazer)

stargazer(m_enef_school, 
          style = "ajps",
          type = "latex",
          coef = list(summary(m_enef_school)$coefficients[,1]),
          title            = "Results of Ordinal Probit Regression",
          covariate.labels = c(names_vec_nov[1:4], 
                               names(m_enef_school$zeta))
          ,
          column.labels = "test",
          #dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement)"
)



```

## Effect over Party: Figure 5a and 5b

The Variable OQ10 (wave 15) covers all the information about the party identification of respondents. 


     1                                                   Lutte Ouvrirre
     2                                       Nouveau Parti Anticapitaliste
     3                                        Parti Communiste Francais
     4                                  France Insoumise / Parti de Gauche
     5                                                      Nouvelle Donne
     6                                                    Parti Socialiste
     7                                             Parti radical de gauche
     8                                         Europe Ecologie - Les Verts
     9 Autres Ecologie : Union des d<e9>mocrates et <e9>cologistes, CAP 21
    10                                                            Le MoDem
    11                                                               L'UDI
    12                                                 Les R<e9>publicains
    13                                                    Debout la France
    14                                                      Front National
    15                                                         Autre parti
    16                                                         En marche 
First, make the same jitter plot as for the German case to see what is the overall preference towards such a school security law. 

```{r}

table(df$OQ10)

df$OQ10 <- as.factor(df$OQ10)

df <- df %>%
  mutate(party_id = recode(OQ10, 
                                    "1" = "Other", #Lutte Ouvrière                                      
                                    "2" = "Other", #Nouveau Parti Anticapitaliste
                                    "3" = "Other", #Parti Communiste Francais
                                    "4" = "Parti de Gauche",
                                    "5" = "Other", #Nouvelle Donne
                                    "6" = "Parti Socialiste",
                                    "7" = "Other",#Parti radical de gauche
                                    "8" = "Les Verts",
                                    "9" = "Other", #Autres Ecologie
                                    "10" = "Le MoDem",
                                    "11" = "L'UDI",
                                    "12" = "Les Républicains",
                                    "13" = "Other", #Debout la France
                                    "14" = "Rassemblement National",
                                    "15" = "Other",
                                    "16" = "En marche!"
  )
  )

prop.table(table(df$party_id, useNA = "ifany"))

df$party_id <-  droplevels(df$party_id)

partyid_int <- as.integer(df$party_id)



#recode for plotting:

df <- df %>%
  mutate(sup_3 = recode(rating_school_factor, 
                             "disagree" = "1",                                  
                             "indifferent" = "2",
                             "agree" = "3"
  )
  ) 

df$sup_3 <- as.numeric(as.character(df$sup_3 ))

pdf(paste(outfolder,"/jitter_party_fr.pdf",sep = ""), width = 8, height = 8)

par(mar  = c(5,11,2,2))


plot(jitter(df$sup_3[df$experiment_groups_school == "Control"]), 
     jitter(partyid_int[df$experiment_groups_school == "Control"]), pch=19, cex=.6,
     xlab="Support for School Security Law", ylab="", axes=F)
axis(1, at = c(1:3), col="white", col.axis="black", labels = c("disagree", "indifferent", "agree"))

axis(2, at=c(1:9), 
     labels= levels(df$party_id), 
     col="white",
     col.axis="black", cex.lab = 0.9, las = 1)

dev.off()



```

Look at Front National Voters:



```{r}

#dummy for front national:

df$front_voter <- ifelse(df$party_id == "Rassemblement National", 1, 0)

table(df$front_voter, useNA = "ifany")

#####################
###Simulate
z.front <- zelig(rating_school_factor ~ experiment_groups_school*front_voter,
               model = "ologit", data = df)

summary(z.front)

#gfcc disapproves

s_gfcc_agree_no_front <- setx(z.front, experiment_groups_school = "Control", front_voter = 0)
s_gfcc_agree_front <- setx(z.front, experiment_groups_school = "Control", front_voter = 1)

#simulate fd
fd_front <- sim(z.front, s_gfcc_agree_no_front,s_gfcc_agree_front)
summary(fd_front)

plot(fd_front)

```

```{r}

s_gfcc_agree_no_front <- setx(z.front, experiment_groups_school = "Control", front_voter = 1)
s_gfcc_agree_front <- setx(z.front, experiment_groups_school = "CC_Disapproves", front_voter = 1)

#simulate fd
fd_front <- sim(z.front, s_gfcc_agree_no_front,s_gfcc_agree_front)
summary(fd_front)

plot(fd_front)


```

Now the same for socialiste:


```{r}

df$socialist_voter <- ifelse(df$party_id == "Parti Socialiste", 1, 0)

table(df$socialist_voter, useNA = "ifany")

#####################
###Simulate
z.socialist <- zelig(rating_school_factor ~ experiment_groups_school*socialist_voter,
                  model = "ologit", data = df)

summary(z.socialist)

#gfcc disapproves

s_gfcc_agree_no_socialist <- setx(z.socialist, experiment_groups_school = "Control", socialist_voter = 0)
s_gfcc_agree_socialist <- setx(z.socialist, experiment_groups_school = "Control", socialist_voter = 1)

#simulate fd
fd_socialist <- sim(z.socialist, s_gfcc_agree_no_socialist,s_gfcc_agree_socialist)
summary(fd_socialist)

plot(fd_socialist)

```


```{r}

s_gfcc_agree_no_socialist <- setx(z.socialist, experiment_groups_school = "Control", socialist_voter = 1)
s_gfcc_agree_socialist <- setx(z.socialist, experiment_groups_school = "CC_Approves", socialist_voter = 1)

#simulate fd
fd_socialist <- sim(z.socialist, s_gfcc_agree_no_socialist,s_gfcc_agree_socialist)
summary(fd_socialist)

plot(fd_socialist)

```

No statistically signifcant effect. 


Plot the FDs for the socialists

```{r}
pdf(paste(outfolder,"/fd_socialist.pdf",sep = ""), width = 12, height = 8)


outcome_vector <- c("Probability of \n disagreeing", "Probability of \n being indifferent", 
                    "Probability of \n agreeing")


par(mfrow=c(1,1), mar=c(5, 6, 2, 1))


plot(colMeans(fd_socialist$sim.out$x1$fd[[1]]), 3:1, 
     pch=c(19),
     ann=F,  
     xlim=c(-0.4, 0.4), 
     #xlabel = "Test",
     # ylim=c(-3.1, 2),
     axes=F,
     cex = 0.8)
     #col="maroon3")
#rect(-2, -2, 2, 2, border=F, col="grey92")
axis(1)
axis(2, at=3:1, label= outcome_vector, col="white", las = 1)

title("", xlab = "FD Socialiste-Voter \n Control Group/CC Approves", ylab = "")
#axis(4, las = 1) 
abline(v=0, lty=2)

fd_ci95 <- apply(fd_socialist$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.025, 0.975))
segments(fd_ci95[1, ], 3:1,
         fd_ci95[2, ], 3:1) # Add 95% Confidence Intervals

fd_ci_90 <- apply(fd_socialist$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.05, 0.95))
segments(fd_ci_90[1, ], 3:1,
         fd_ci_90[2, ], 3:1,
         lwd = 2) # Add 90% Confidence Intervals

dev.off()

```

```{r}

pdf(paste(outfolder,"/fd_front_national.pdf",sep = ""), width = 12, height = 8)
par(mfrow=c(1,1), mar=c(5, 6, 2, 1))
#Plot Front National

plot(colMeans(fd_front$sim.out$x1$fd[[1]]), 3:1, 
     pch=c(19),
     ann=F,  
     xlim=c(-0.4, 0.4), 
     axes=F, 
     cex = 0.8)

axis(1)
axis(2, at=3:1, label= outcome_vector, col="white", las = 1)

title("", xlab = "FD FN-Voter \n Control Group/CC Disapproves", ylab = "")
#axis(4, las = 1) 
abline(v=0, lty=2)

fd_ci_95 <- apply(fd_front$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.025, 0.975))
segments(fd_ci_95[1, ], 3:1,
         fd_ci_95[2, ], 3:1) # Add 95% Confidence Intervals

fd_ci_90 <- apply(fd_front$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.05, 0.95))
segments(fd_ci_90[1, ], 3:1,
         fd_ci_90[2, ], 3:1,
         lwd = 2) # Add 95% Confidence Intervals

dev.off()

```
