---
title: "Robustness France"
author: "Sebastian Sternberg"
date: "9/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Robustness France


## Knowledge of Court:

The variable PCONINS_3 covers the question whether respondents know the court or not. 

Wording: Voici une liste d&#39;institutions de la République. Pour chacune d&#39;entre-elles, dites si: 
1 Vous la connaissez de nom et vous êtes informé sur ses fonctions
2 Vous la connaissez de nom mais vous n&#39;êtes pas informé sur ses fonctions
3 Vous ne la connaissez pas


```{r}

rm(list = ls())

require(magrittr)
require(haven)
require(foreign)
require(dplyr)

library(tidyverse)


```


# Data Prep


```{r}



df <- read_dta("../Data/ENEF2017_legitimacy_experiment.dta")


table(df$QEXPPOSINS, useNA = "ifany") #experimental groups pension

table(df$PEXPPOSINS, useNA = "ifany") #experimental groups school 


#Recode experimental groups:

class(df$ID12)
class(df$QEXPPOSINS)


df$PEXPPOSINS <- as.factor(df$PEXPPOSINS)

#recode the education variable

df <- df %>%
  mutate(experiment_groups_school = recode(PEXPPOSINS, 
                                    "1" = "Control",                                       
                                    "2" = "CC_Approves",
                                    "3" = "CC_Disapproves",
                                    "4" = "Haut_Conseil_Edu_Approves",
                                    "5" = "Haut_Conseil_Edu_Disapproves"
  )
  )


df$QEXPPOSINS <- as.factor(df$QEXPPOSINS)

#recode the pension variable
df <- df %>%
  mutate(experiment_groups_pension = recode(QEXPPOSINS, 
                                    "1" = "Control",                                       
                                    "2" = "CC_Approves",
                                    "3" = "CC_Disapproves",
                                    "4" = "Conseil_d_Orientation_appr.",
                                    "5" = "Conseil_d_Orientation_disappr."
  )
  )


#recode NAs
df$PCCFAITH[df$PCCFAITH > 6] <- NA
df$QCCFAITH[df$QCCFAITH > 6] <- NA

table(df$PCCFAITH, useNA = "ifany")
table(df$QCCFAITH, useNA = "ifany")


#short check:

#first reverse to have the German coding:

df$PCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_school  = recode(PCCFAITH, 
                             "1" = "5",                                  
                             "2" = "4",
                             "3" = "3",
                             "4" = "2",
                             "5" = "1"
  )
  ) 
#order levels again

df$rating_school <- factor(df$rating_school, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_school, df$PCCFAITH)


###do the same for the pension variable

df$QCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_pension  = recode(QCCFAITH, 
                             "1" = "5",                                  
                             "2" = "4",
                             "3" = "3",
                             "4" = "2",
                             "5" = "1"
  )
  ) 
#order levels again

df$rating_pension <- factor(df$rating_pension, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_pension, df$QCCFAITH)


#################
#continue recoding: now to 3-point scale

df <- df %>%
  mutate(rating_school_factor = recode(rating_school, 
                             "1" = "disagree",                                  
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_school, df$rating_school_factor, useNA = "ifany")


#same for pension policy experiment

df <- df %>%
  mutate(rating_pension_factor = recode(rating_pension, 
                             "1" = "disagree",                                  
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_pension, df$rating_pension_factor, useNA = "ifany")


```


## Robustness Check Different Policy Issue ENEF, France


```{r}
m_enef_pension <- polr(rating_pension_factor ~ experiment_groups_pension, 
                   data = df, 
               method = "probit",
                   Hess=TRUE)

summary(m_enef_pension)

#pvalues

(ctable <- coef(summary(m_enef_pension)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))


```


```{r}
names_vec_nov <- c("CC \n Approves", 
                   "CC \n Disapproves", 
                   "Haut Conseil \n de l'Éducation \n Approves", 
                   "Haut Conseil \n de l'Éducation \n Disapproves", " ", " ")

stargazer(m_enef_pension, 
          style = "ajps",
          type = "latex",
                    coef = list(summary(m_enef_pension)$coefficients[,1]),
          title            = "Results of Ordinal Probit Regression",
          covariate.labels = c(names_vec_nov[1:4], 
                               names(m_enef_pension$zeta))
          ,
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Pension Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Standard errors clustered by respondent."
)



```


# Knowledge Robustness CC


```{r}
df$PCONINS_3[df$PCONINS_3 > 11] <- NA

prop.table(table(df$PCONINS_3, useNA = "ifany"))


df$know_france <- ifelse(df$PCONINS_3 == 1, 1, 0)
table(df$know_france)
prop.table(table(df$know_france, useNA = "ifany"))

#Run model:

enef_know_ia <- polr(rating_school_factor ~ experiment_groups_school*know_france,
                     method = "probit",
                       Hess=TRUE,
                     data = df)

summary(enef_know_ia)


#pvalues

ctable <- coef(summary(enef_know_ia))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))

#Nothing significant. Make table:

stargazer(enef_know_ia, 
          style = "ajps",
          type = "latex",
          coef = list(summary(enef_know_ia)$coefficients[,1]),
          title            = "Results of Ordinal Probit Regression",
          column.labels = "test",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatment group. The baseline category is the control group (no treatment)"
)

```

## School Policy with 5 point scale:

```{r}
m_enef_school_5 <- polr(rating_school ~ experiment_groups_school, 
                       data = df, 
                       method = "probit",
                       Hess=TRUE)

summary(m_enef_school_5)

#pvalues

(ctable <- coef(summary(m_enef_school_5)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))

#make regression table:

names_vec_nov <- c("CC \n Approves", 
                   "CC \n Disapproves", 
                   "Haut Conseil \n de l'Éducation \n Approves", 
                   "Haut Conseil \n de l'Éducation \n Disapproves", " ", " ")


stargazer(m_enef_school_5, 
          style = "ajps",
          type = "latex",
          coef = list(summary(m_enef_school_5)$coefficients[,1]),
          title            = "Results of Ordinal Probit Regression",
          covariate.labels = c(names_vec_nov[1:4], 
                               names(m_enef_school_5$zeta))
          ,
          column.labels = "test",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatment group. The baseline category is the control group (no treatment)"
)


```




