---
title: "Gip Analysis Germany"
author: "Sebastian Sternberg"
date: "02 08 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

rm(list = ls())

require(MASS)
require(zeligverse)
require(magrittr)
require(dplyr)
require(stargazer)

load("../Data/gip_merge.Rda")


```

## Table 1 & Jitterplot

```{r}
gip_merge$experiment_groups_jan <- as.character(gip_merge$experiment_groups_jan)
gip_merge$experiment_groups_nov <- as.character(gip_merge$experiment_groups_nov)

#create outcome vector

response_vector <- c(gip_merge$sup_factor_nov, gip_merge$sup_factor_jan)

#back to factor
response_vector <- as.factor(response_vector)

#create experimental group vector

experiment_gr <- c(gip_merge$experiment_groups_nov, gip_merge$experiment_groups_jan)

#as factor as well  
experiment_gr <- as.factor(experiment_gr)

#ids for clustered SEs:

ids_gip <- as.factor(c(gip_merge$id_g, gip_merge$id_g))

#create new data set:

gip_analysis <- cbind.data.frame(ids_gip, experiment_gr, response_vector)

#omit NAs for clustered SE estimation

gip_analysis <- na.omit(gip_analysis) #get rid of NAs. These are the respondents who refused to answer or did not answer


#recode outcome :

gip_analysis <- gip_analysis %>%
  mutate(response_vector = recode(response_vector, 
                                  "1" = "disagree",                                  
                                  "2" = "indifferent",
                                  "3" = "agree"
  )
  ) 

#check order: important for later that the direction of the regression is in line with the order of the factor:

levels(gip_analysis$response_vector) #check
merge_trust_gov <- data.frame(ids_gip = as.factor(gip_merge$id_g), trust_gov = as.numeric(gip_merge$AK27034))

gip_analysis <- left_join(gip_analysis,merge_trust_gov)


party_affiliation_merge <- data.frame(ids_gip = as.factor(gip_merge$id_g), AA25039 = as.factor(gip_merge$AA25039))


#recode sunday_election
gip_analysis <- left_join(gip_analysis, party_affiliation_merge)

gip_analysis$AA25039[gip_analysis$AA25039 < 0] <- NA
gip_analysis$AA25039[gip_analysis$AA25039 == "1"] <- NA
gip_analysis$AA25039[gip_analysis$AA25039 == "2"] <- NA

gip_analysis <- gip_analysis %>%
  mutate(sunda_election = recode(as.factor(AA25039), 
                                 "3" = "CDU/CSU",
                                 "4" = "SPD",
                                 "5" = "FDP",
                                 "6" = "Greens",
                                 "7" = "Lefts",
                                 "8" = "Other", #NPD
                                 "9" = "Other", #Piraten
                                 "10" = "Other",
                                 "11" = "AfD"
  )
  )

gip_analysis$sunda_election[gip_analysis$sunda_election ==  "NA"] <- NA
gip_analysis$sunda_election[gip_analysis$sunda_election ==  "-99"] <- NA
gip_analysis$sunda_election[gip_analysis$sunda_election ==  "-98"] <- NA


#drop unused levels:

gip_analysis$sunda_election <-  droplevels(gip_analysis$sunda_election)

table(gip_analysis$sunda_election, useNA = "ifany")
sunda_election_int <- as.integer(gip_analysis$sunda_election)


#recode for plotting:

gip_analysis <- gip_analysis %>%
  mutate(sup_3 = recode(response_vector, 
                        "disagree" = "1",                                  
                        "indifferent" = "2",
                        "agree" = "3"
  )
  ) 

gip_analysis$sup_3 <- as.numeric(as.character(gip_analysis$sup_3 ))


par(mar  = c(4,6,2,2))


plot(jitter(gip_analysis$sup_3[gip_analysis$experiment_gr == "Control"]), 
     jitter(sunda_election_int[gip_analysis$experiment_gr == "Control"]), pch=19, cex=.6,
     xlab="Support for School Security Law", ylab="", axes=F)
axis(1, at = c(1:3), col="white", col.axis="black", labels = c("disagree", "indifferent", "agree"))

axis(2, at=c(1:7), 
     labels= levels(gip_analysis$sunda_election), 
     col="white",
     col.axis="black", cex.lab = 0.9, las = 1)



table_germany <- round(prop.table(table(
  gip_analysis$sunda_election[gip_analysis$experiment_gr == "Control"],
      gip_analysis$response_vector[gip_analysis$experiment_gr == "Control"])
), 3)*100


write.table(table_germany, file = "table_germany_supportoverparty.txt", sep = ",", quote = FALSE, row.names = F)

#########################
#now the same for France:
df <- read_dta("../Data/ENEF2017_legitimacy_experiment.dta")

#Recode experimental groups:

class(df$ID12)
class(df$QEXPPOSINS)


df$PEXPPOSINS <- as.factor(df$PEXPPOSINS)

#recode the education variable

df <- df %>%
  mutate(experiment_groups_school = recode(PEXPPOSINS, 
                                           "1" = "Control",                   
                                           "2" = "CC_Approves",
                                           "3" = "CC_Disapproves",
                                           "4" = "Haut_Conseil_Edu_Approves",
                                           "5" = "Haut_Conseil_Edu_Disapproves"
  )
  )


df$QEXPPOSINS <- as.factor(df$QEXPPOSINS)

#recode the pension variable
df <- df %>%
  mutate(experiment_groups_pension = recode(QEXPPOSINS, 
                                            "1" = "Control",                                       
                                            "2" = "CC_Approves",
                                            "3" = "CC_Disapproves",
                                            "4" = "Conseil_d_Orientation_appr.",
                                            "5" = "Conseil_d_Orientation_disappr."
  )
  )


#recode NAs
df$PCCFAITH[df$PCCFAITH > 6] <- NA
df$QCCFAITH[df$QCCFAITH > 6] <- NA

table(df$PCCFAITH, useNA = "ifany")
table(df$QCCFAITH, useNA = "ifany")


#short check:

#first reverse to have the German coding:

df$PCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_school  = recode(PCCFAITH, 
                                 "1" = "5",                                  
                                 "2" = "4",
                                 "3" = "3",
                                 "4" = "2",
                                 "5" = "1"
  )
  ) 
#order levels again

df$rating_school <- factor(df$rating_school, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_school, df$PCCFAITH)


###do the same for the pension variable

df$QCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_pension  = recode(QCCFAITH, 
                                  "1" = "5",                                  
                                  "2" = "4",
                                  "3" = "3",
                                  "4" = "2",
                                  "5" = "1"
  )
  ) 
#order levels again

df$rating_pension <- factor(df$rating_pension, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_pension, df$QCCFAITH)


#################
#continue recoding: now to 3-point scale

df <- df %>%
  mutate(rating_school_factor = recode(rating_school, 
                                       "1" = "disagree",                                  
                                       "2" = "disagree",
                                       "3" = "indifferent",
                                       "4" = "agree",
                                       "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_school, df$rating_school_factor, useNA = "ifany")


#same for pension policy experiment

df <- df %>%
  mutate(rating_pension_factor = recode(rating_pension, 
                                        "1" = "disagree",                                  
                                        "2" = "disagree",
                                        "3" = "indifferent",
                                        "4" = "agree",
                                        "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_pension, df$rating_pension_factor, useNA = "ifany")
df$OQ10 <- as.factor(df$OQ10)

df <- df %>%
  mutate(party_id = recode(OQ10, 
                           "1" = "Other", #Lutte Ouvri?re                                      
                           "2" = "Other", #Nouveau Parti Anticapitaliste
                           "3" = "Other", #Parti Communiste Francais
                           "4" = "Parti de Gauche",
                           "5" = "Other", #Nouvelle Donne
                           "6" = "Parti Socialiste",
                           "7" = "Other",#Parti radical de gauche
                           "8" = "Les Verts",
                           "9" = "Other", #Autres Ecologie
                           "10" = "Le MoDem",
                           "11" = "L'UDI",
                           "12" = "Les R?publicains",
                           "13" = "Other", #Debout la France
                           "14" = "Rassemblement National",
                           "15" = "Other",
                           "16" = "En marche!"
  )
  )

prop.table(table(df$party_id, useNA = "ifany"))

df$party_id <-  droplevels(df$party_id)

partyid_int <- as.integer(df$party_id)



#recode for plotting:

df <- df %>%
  mutate(sup_3 = recode(rating_school_factor, 
                        "disagree" = "1",                                  
                        "indifferent" = "2",
                        "agree" = "3"
  )
  ) 

df$sup_3 <- as.numeric(as.character(df$sup_3 ))


df$QCONF4_2_fac <- as.factor(df$QCONF4_2)

df <- df %>%
  mutate(trust_cc = recode(QCONF4_2_fac, 
                           "0" = "no trust at all",                                       
                           "1" = "no trust at all",
                           "2" = "no trust at all",
                           "3" = "no trust",
                           "4" = "rather not trust",
                           "5" = "indifferent",
                           "6" = "rather trust",
                           "7" = "high trust",
                           "8" = "very high trust",
                           "9" = "very high trust",
                           "10" = "very high trust"
  )
  )

table(df$trust_cc, df$QCONF4_2_fac)

#Recode to numeric:

df <- df %>%
  mutate(trust_cc_num = recode(trust_cc, 
                               "no trust at all" = "1",
                               "no trust" = "2",
                               "rather not trust" = "3",
                               "indifferent" = "4",
                               "rather trust" = "5",
                               "high trust" = "6",
                               "very high trust" = "7"
  )
  )

df$trust_cc_num <- as.numeric(as.character(df$trust_cc_num))

df$trust_cc_num[df$trust_cc_num > 11] <- NA

table(df$trust_cc_num, useNA = "ifany")
table(df$trust_cc)

df$OQ10 <- as.factor(df$OQ10)

df <- df %>%
  mutate(party_id = recode(OQ10, 
                           "1" = "Other", #Lutte Ouvri?re                                      
                           "2" = "Other", #Nouveau Parti Anticapitaliste
                           "3" = "Other", #Parti Communiste Francais
                           "4" = "Parti de Gauche",
                           "5" = "Other", #Nouvelle Donne
                           "6" = "Parti Socialiste",
                           "7" = "Other",#Parti radical de gauche
                           "8" = "Les Verts",
                           "9" = "Other", #Autres Ecologie
                           "10" = "Le MoDem",
                           "11" = "L'UDI",
                           "12" = "Les R?publicains",
                           "13" = "Other", #Debout la France
                           "14" = "Rassemblement National",
                           "15" = "Other",
                           "16" = "En marche!"
  )
  )

prop.table(table(df$party_id, useNA = "ifany"))

df$party_id <-  droplevels(df$party_id)

partyid_int <- as.integer(df$party_id)



#recode for plotting:

df <- df %>%
  mutate(sup_3 = recode(rating_school_factor, 
                        "disagree" = "1",                                  
                        "indifferent" = "2",
                        "agree" = "3"
  )
  ) 

df$sup_3 <- as.numeric(as.character(df$sup_3 ))



table_france <- round(prop.table(table(
  df$party_id[df$experiment_groups_school == "Control"],
  df$rating_school_factor[df$experiment_groups_school == "Control"])
  ), 3)*100


write.table(table_france, file = "table_france_supportoverparty.txt", sep = ",", quote = FALSE, row.names = F)



```



## Figure 2:

Set up the data for the ordered probit:

```{r}

gip_merge$experiment_groups_jan <- as.character(gip_merge$experiment_groups_jan)
gip_merge$experiment_groups_nov <- as.character(gip_merge$experiment_groups_nov)

#create outcome vector

response_vector <- c(gip_merge$sup_factor_nov, gip_merge$sup_factor_jan)

#back to factor
response_vector <- as.factor(response_vector)

#create experimental group vector

experiment_gr <- c(gip_merge$experiment_groups_nov, gip_merge$experiment_groups_jan)
  
#as factor as well  
experiment_gr <- as.factor(experiment_gr)

#ids for clustered SEs:

ids_gip <- as.factor(c(gip_merge$id_g, gip_merge$id_g))

#create new data set:

gip_analysis <- cbind.data.frame(ids_gip, experiment_gr, response_vector)

#omit NAs for clustered SE estimation

gip_analysis <- na.omit(gip_analysis) #get rid of NAs. These are the respondents who refused to answer or did not answer


#recode outcome :

gip_analysis <- gip_analysis %>%
  mutate(response_vector = recode(response_vector, 
                             "1" = "disagree",                                
                             "2" = "indifferent",
                             "3" = "agree"
  )
  ) 

#check order: important for later that the direction of the regression is in line with the order of the factor:

levels(gip_analysis$response_vector) #check


```

Estimate an ordered probit regression. Afterwards, make a coefficient plot. 

```{r}
#estimate ordered probit:

m_gip_basic <- polr(response_vector ~ experiment_gr,
                    data = gip_analysis,
                    method = "probit",
                   Hess=TRUE)

summary(m_gip_basic)

#pvalues

(ctable <- coef(summary(m_gip_basic)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))


#estimate clustered SEs:

library(lmtest)
library(sandwich)

ses_m_gip_basic <- coeftest(m_gip_basic, vcov=vcovCL(m_gip_basic, factor(gip_analysis$ids_gip) ))

###plot coefs:

coef_vec <- summary(m_gip_basic)$coefficients[1:6,1]   # Extract coefficient estimates
coef_vec <- c(coef_vec[3:4], coef_vec[5:6], coef_vec[1:2]) #reorder so that GFCC is first


names_vec<- c("GFCC \n Approves", 
                   "GFCC \n Disapproves", 
                                 "Conference of the \n Ministers of Education \n  Approves", 
                   "Conference of the \n Ministers of Education \n Disapproves", 
                                 "Data Security \n Official Approves",     
              "Data Security \n Official Disapproves")

#get clustered SEs:

se_vec <- ses_m_gip_basic[1:6,2]
se_vec <- c(se_vec[3:4], se_vec[5:6], se_vec[1:2]) #reorder so that GFCC is first

#outfolder to save
outfolder <- ("../Figures")


pdf(paste(outfolder,"/coefplot_gip_base.pdf",sep = ""), width = 8, height = 8)

#adjust margins:
par(mar  = c(4,10,2,2))

plot(coef_vec, length(coef_vec):1, 
     pch=19, 
     cex=.8, 
     axes=F, 
     ylab="", 
     xlab="Ordered Probit Coefficients", 
     xlim=c(-0.7, 0.7))
axis(1)
axis(2, at=length(coef_vec):1, label=names_vec, col="white", las = 1)
abline(v=0, lty=2) # add zero reference line

#plot 95% CIs
segments(coef_vec - qnorm(0.975)*se_vec,  length(coef_vec):1, coef_vec + qnorm(0.975)*se_vec, length(coef_vec):1) # add confidence intervals

#add 90% CIs
segments(coef_vec - qnorm(0.95)*se_vec,  length(coef_vec):1, coef_vec + qnorm(0.95)*se_vec, length(coef_vec):1, lwd = 2) # add confidence intervals

dev.off()

```

Make latex table for Appendix mit clusted SEs per respondent ID:

```{r}


stargazer(m_gip_basic, 
          style = "ajps",
          type = "latex",
          coef = list(summary(m_gip_basic)$coefficients[,1]),
           se = list(ses_m_gip_basic[,2]),
          #t = ses_m_gip_basic[,3],
          p = list(ses_m_gip_basic[, 4]),
          title            = "Results of Ordinal Probit Regression",
          covariate.labels = c(names_vec, 
                               names(m_gip_basic$zeta)),
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Standard errors clustered by respondent."
)

```

## Quantities of Interests: Figure 3

For us, not the raw coefficients are per se interesting, but even more so the first differences between the treatement groups. That is, the effect between the GFCC approving and disapproving, and the same for the Minister of education.

Treatment effect is the difference between the control group and the gfcc approves or disapproves group:

```{r}

z_gfcc_treatment_effect <- zelig(response_vector ~ experiment_gr,
               model = "oprobit", 
               data = gip_analysis)

summary(z_gfcc_treatment_effect)

#set up scenarios:

s_control <- setx(z_gfcc_treatment_effect, experiment_gr = "Control") #control group
s_gfcc_agree <- setx(z_gfcc_treatment_effect, experiment_gr = "GFCC_Approves") #gfcc_agrees


fd_control_agree <- sim(z_gfcc_treatment_effect, s_control,s_gfcc_agree) #simulate and calculate fd
plot(fd_control_agree)

```

Similar simulation but with GFCC disapproves, using the same model:

```{r}

s_control <- setx(z_gfcc_treatment_effect, experiment_gr = "Control") #control group
s_gfcc_disagrees <- setx(z_gfcc_treatment_effect, experiment_gr = "GFCC_Disapproves") #gfcc_agrees


fd_control_disagree <- sim(z_gfcc_treatment_effect, s_control,s_gfcc_disagrees) #simulate and calculate fd
summary(fd_control_disagree)
plot(fd_control_disagree)


```


Make plot of FDs:

```{r}
mean_fd_control_gfccdisapp<- colMeans(fd_control_disagree$sim.out$x1$fd[[1]])

outcome_vector <- c("Probability of \n disagreeing", "Probability of \n being indifferent", 
                    "Probability of \n agreeing")

pdf(paste(outfolder,"/fd_control_disapprv.pdf",sep = ""), width = 6, height = 6)

par(mar=c(5, 6, 2, 0))

plot(mean_fd_control_gfccdisapp, 3:1, 
     pch=c(19),
     ann=F,  
     xlim=c(-0.1, 0.1), 
     #xlabel = "Test",
     # ylim=c(-3.1, 2),
     axes=F,
     cex = 0.8)
     #col="maroon3")
#rect(-2, -2, 2, 2, border=F, col="grey92")
axis(1)
axis(2, at=3:1, label= outcome_vector, col="white", las = 1)

title("", xlab = "First Difference  \n Control Group vs. GFCC Approves", ylab = "")
#axis(4, las = 1) 
abline(v=0, lty=2)

fd_ci95 <- apply(fd_control_disagree$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.025, 0.975))
segments(fd_ci95[1, ], 3:1,
         fd_ci95[2, ], 3:1) # Add 95% Confidence Intervals

fd_ci_90 <- apply(fd_control_disagree$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.05, 0.95))
segments(fd_ci_90[1, ], 3:1,
         fd_ci_90[2, ], 3:1,
         lwd = 2) # Add 95% Confidence Intervals

dev.off()

```

Plot the FD in one graph

```{r}
mean_fd_control_gfccapp<- colMeans(fd_control_agree$sim.out$x1$fd[[1]])


pdf(paste(outfolder,"/fd_control_apprv.pdf",sep = ""), width = 6, height = 6)

par(mar=c(5, 6, 2, 0))

plot(mean_fd_control_gfccapp, 3:1, 
     pch=c(19),
     ann=F,  
     xlim=c(-0.1, 0.1), 
     #xlabel = "Test",
     # ylim=c(-3.1, 2),
     axes=F,
     cex = 0.8)
     #col="maroon3")
#rect(-2, -2, 2, 2, border=F, col="grey92")
axis(1)
axis(2, at=3:1, label= outcome_vector, col="white", las = 1)

title("", xlab = "First Difference  \n Control Group vs. GFCC Approves", ylab = "")
#axis(4, las = 1) 
abline(v=0, lty=2)

fd_ci95 <- apply(fd_control_agree$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.025, 0.975))
segments(fd_ci95[1, ], 3:1,
         fd_ci95[2, ], 3:1) # Add 95% Confidence Intervals

fd_ci_90 <- apply(fd_control_agree$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.05, 0.95))
segments(fd_ci_90[1, ], 3:1,
         fd_ci_90[2, ], 3:1,
         lwd = 2) # Add 95% Confidence Intervals

dev.off()

```

## Figure 4a and 4b

Effect of GFCC treatment on partisans of the AfD and Greens

```{r}

party_affiliation_merge <- data.frame(ids_gip = as.factor(gip_merge$id_g), AA25039 = as.factor(gip_merge$AA25039))


#recode sunday_election
gip_analysis <- left_join(gip_analysis, party_affiliation_merge)

gip_analysis$AA25039[gip_analysis$AA25039 < 0] <- NA
gip_analysis$AA25039[gip_analysis$AA25039 == "1"] <- NA
gip_analysis$AA25039[gip_analysis$AA25039 == "2"] <- NA

gip_analysis <- gip_analysis %>%
     mutate(sunda_election = recode(as.factor(AA25039), 
         "3" = "CDU/CSU",
         "4" = "SPD",
         "5" = "FDP",
         "6" = "Greens",
         "7" = "Lefts",
         "8" = "Other", #NPD
         "9" = "Other", #Piraten
         "10" = "Other",
         "11" = "AfD"
     )
)

gip_analysis$sunda_election[gip_analysis$sunda_election ==  "NA"] <- NA
gip_analysis$sunda_election[gip_analysis$sunda_election ==  "-99"] <- NA
gip_analysis$sunda_election[gip_analysis$sunda_election ==  "-98"] <- NA


#drop unused levels:

gip_analysis$sunda_election <-  droplevels(gip_analysis$sunda_election)

table(gip_analysis$sunda_election, useNA = "ifany")
sunda_election_int <- as.integer(gip_analysis$sunda_election)


#recode for plotting:

gip_analysis <- gip_analysis %>%
  mutate(sup_3 = recode(response_vector, 
                             "disagree" = "1",
                             "indifferent" = "2",
                             "agree" = "3"
  )
  ) 

gip_analysis$sup_3 <- as.numeric(as.character(gip_analysis$sup_3 ))


outfolder <- ("../Figures")

pdf(paste(outfolder,"/jitter_party_ger.pdf",sep = ""), width = 8, height = 8)

par(mar  = c(4,6,2,2))


plot(jitter(gip_analysis$sup_3[gip_analysis$experiment_gr == "Control"]), jitter(sunda_election_int[gip_analysis$experiment_gr == "Control"]), pch=19, cex=.6,
     xlab="Support for School Security Law", ylab="", axes=F)
axis(1, at = c(1:3), col="white", col.axis="black", labels = c("disagree", "indifferent", "agree"))

axis(2, at=c(1:7), 
     labels= levels(gip_analysis$sunda_election), 
     col="white",
     col.axis="black", cex.lab = 0.9, las = 1)

dev.off()

```

## Figure 4a

Look at AfD Voters only:

```{r}

#dummy for AfD:

gip_analysis$afd_voter <- ifelse(gip_analysis$sunda_election == "AfD", 1, 0)

table(gip_analysis$afd_voter, useNA = "ifany")

#run model
m_afd_dummy <- polr(response_vector ~ experiment_gr*afd_voter, 
                   data = gip_analysis, 
                   Hess=TRUE)

summary(m_afd_dummy)

#pvalues

(ctable <- coef(summary(m_afd_dummy)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))

#####################
###Simulate
z.afd <- zelig(response_vector ~ experiment_gr*afd_voter,
               model = "ologit", data = gip_analysis)

summary(z.afd)

#gfcc disapproves

s_gfcc_agree_no_afd <- setx(z.afd, experiment_gr = "GFCC_Disapproves", afd_voter = 0)
s_gfcc_agree_afd <- setx(z.afd, experiment_gr = "GFCC_Disapproves", afd_voter = 1)

#simulate fd
fd_afd <- sim(z.afd, s_gfcc_agree_no_afd,s_gfcc_agree_afd)
summary(fd_afd)

plot(fd_afd)

```

Compare control group AfD with court disapproving policy:

```{r}

s_gfcc_agree_no_afd <- setx(z.afd, experiment_gr = "Control", afd_voter = 1)
s_gfcc_agree_afd <- setx(z.afd, experiment_gr = "GFCC_Disapproves", afd_voter = 1)

#simulate fd
fd_afd <- sim(z.afd, s_gfcc_agree_no_afd,s_gfcc_agree_afd)
summary(fd_afd)

plot(fd_afd)

```

Make regression table for the Appendix of the models.

```{r}

gip_analysis$afd_voter <- ifelse(gip_analysis$sunda_election == "AfD", 1, 0)

#ommit NAs because cluster function cannot handle them

afd_data <- data.frame(afd_voter = gip_analysis$afd_voter, response_vector = gip_analysis$response_vector,
                       experiment_gr = gip_analysis$experiment_gr, ids_gip = gip_analysis$ids_gip) %>% na.omit

#run model
m_afd_dummy <- polr(response_vector ~ experiment_gr*afd_voter, 
                   data = afd_data, 
                   Hess=TRUE)

ses_m_gip_afddummy <- coeftest(m_afd_dummy, vcov=vcovCL(m_afd_dummy, factor(afd_data$ids_gip)))


names_vec_afd <- c("Data Security Official Approves","Data Security Official Disapproves",
                               "GFCC Approves", 
                   "GFCC Disapproves", 
                                "Conference of the Ministers of Education Approves", 
                               "Conference of the Ministers of Education Disapproves","AfD Voter (=1)")

#create interaction names

names_vec_afd_ia <- NA

for(i in 1:(length(names_vec_afd)-1)){
  
names_vec_afd_ia[i] <-  paste(names_vec_afd[i], "X AfD-Voter")
  
}


#make regression table
stargazer(m_afd_dummy, 
          style = "ajps",
          type = "latex",
          coef = list(summary(m_afd_dummy)$coefficients[,1]),
           se = list(ses_m_gip_afddummy[,2]),
          #t = ses_m_gip_basic[,3],
          p = list(ses_m_gip_afddummy[, 4]),
          title            = "Results of Ordinal Probit Regression",
          covariate.labels = c(names_vec_afd, names_vec_afd_ia,
                              names(m_afd_dummy$zeta)),
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Standard errors clustered by respondent."
)



```

Plot AfD results:

```{r}
pdf(paste(outfolder,"/fd_afd1.pdf",sep = ""), width = 12, height = 8)

par(mar=c(5, 6, 2, 1))
plot(colMeans(fd_afd$sim.out$x1$fd[[1]]), 3:1, 
     pch=c(19),
     ann=F,  
     xlim=c(-0.5, 0.5), 
     axes=F, 
     cex = 0.8)

axis(1)
axis(2, at=3:1, label= outcome_vector, col="white", las = 1)

title("", xlab = "FD AfD-Partisans \n Control Group versus GFCC Disapproves", ylab = "")

abline(v=0, lty=2)

fd_ci_95 <- apply(fd_afd$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.025, 0.975))
segments(fd_ci_95[1, ], 3:1,
         fd_ci_95[2, ], 3:1,
         lwd = 1) # Add 95% Confidence Intervals

fd_ci_90 <- apply(fd_afd$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.05, 0.95))
segments(fd_ci_90[1, ], 3:1,
         fd_ci_90[2, ], 3:1,
         lwd = 3) # Add 90% Confidence Intervals

dev.off()


```

Dummy for Greens:

```{r}

#dummy for Greens:
gip_analysis$green_voter <- ifelse(gip_analysis$sunda_election == "Greens", 1, 0)

table(gip_analysis$green_voter, useNA = "ifany")

#run model
m_green_dummy <- polr(response_vector ~ experiment_gr*green_voter, 
                    data = gip_analysis, 
                    Hess=TRUE)

summary(m_green_dummy)

#pvalues

(ctable <- coef(summary(m_green_dummy)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))

#####################
###Simulate
z.greens <- zelig(response_vector ~ experiment_gr*green_voter,
               model = "ologit", data = gip_analysis)

summary(z.greens)

#gfcc disapproves

s_gfcc_agree_no_green <- setx(z.greens, experiment_gr = "Control", green_voter = 0)
s_gfcc_agree_green <- setx(z.greens, experiment_gr = "GFCC_Approves", green_voter = 1)

#simulate fd
fd_greens <- sim(z.greens, s_gfcc_agree_no_green,s_gfcc_agree_green)
summary(fd_greens)

plot(fd_greens)

```

Make regression table for Appendix:


```{r}

#ommit NAs because cluster function cannot handle them

green_data <- data.frame(green_voter = gip_analysis$green_voter, response_vector = gip_analysis$response_vector,
                       experiment_gr = gip_analysis$experiment_gr, ids_gip = gip_analysis$ids_gip) %>% na.omit

#run model
m_green_dummy <- polr(response_vector ~ experiment_gr*green_voter, 
                    data = green_data, 
                    Hess=TRUE)

ses_m_gip_greendummy <- coeftest(m_green_dummy, vcov=vcovCL(m_green_dummy, factor(green_data$ids_gip)))


names_vec_greens <- c("Data Security Official Approves","Data Security Official Disapproves",
                               "GFCC Approves", 
                   "GFCC Disapproves", 
                                "Conference of the Ministers of Education Approves", 
                               "Conference of the Ministers of Education Disapproves","Green Voter (=1)")

#create interaction names

names_vec_greens_ia <- NA

for(i in 1:(length(names_vec_greens)-1)){
  
names_vec_greens_ia[i] <-  paste(names_vec_greens[i], "X Green-Voter")
  
}


#make regression table
stargazer(m_green_dummy, 
          style = "ajps",
          type = "latex",
          coef = list(summary(m_green_dummy)$coefficients[,1]),
           se = list(ses_m_gip_greendummy[,2]),
          #t = ses_m_gip_basic[,3],
          p = list(ses_m_gip_greendummy[, 4]),
          title            = "Results of Ordinal Probit Regression",
          covariate.labels = c(names_vec_greens, names_vec_greens_ia,
                              names(m_green_dummy$zeta)),
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Standard errors clustered by respondent."
)


```


Plot it:


```{r}

s_gfcc_agree_no_green <- setx(z.greens, experiment_gr = "Control", green_voter = 1)
s_gfcc_agree_green <- setx(z.greens, experiment_gr = "GFCC_Approves", green_voter = 1)

#simulate fd
fd_greens <- sim(z.greens, s_gfcc_agree_no_green,s_gfcc_agree_green)
summary(fd_greens)

plot(fd_greens)


```


Plot results for the Greens:

```{r}

pdf(paste(outfolder,"/fd_greens1.pdf",sep = ""), width = 12, height = 8)

par(mar=c(5, 6, 2, 1))
plot(colMeans(fd_greens$sim.out$x1$fd[[1]]), 3:1, 
     pch=c(19),
     ann=F,  
     xlim=c(-0.5, 0.5), 
     axes=F, 
     cex = 0.8)

axis(1)
axis(2, at=3:1, label= outcome_vector, col="white", las = 1)

title("", xlab = "FD Greens-Partisans \n Control Group versus GFCC Approves", ylab = "")
#axis(4, las = 1) 
abline(v=0, lty=2)

fd_ci_95 <- apply(fd_greens$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.025, 0.975))
segments(fd_ci_95[1, ], 3:1,
         fd_ci_95[2, ], 3:1) # Add 95% Confidence Intervals

fd_ci_90 <- apply(fd_greens$sim.out$x1$fd[[1]], 2, quantile, probs = c(0.05, 0.95))
segments(fd_ci_90[1, ], 3:1,
         fd_ci_90[2, ], 3:1,
         lwd = 3) # Add 95% Confidence Intervals

dev.off()

```








