---
title: "Robustness GIP"
author: "Sebastian Sternberg"
date: "14 Januar 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}

rm(list = ls())

require(magrittr)
require(haven)
require(foreign)
require(dplyr)


```


```{r}

gip_nov <- read_dta("../Data/GIP_W26_V2.dta")

#subset only the necessary variables for experiment

gip_nov <- gip_nov %>%
  dplyr::select(id_g, 
                expAK26001_1, #experimental groups
                AK26001, #outcome experiment
                AK26023, # amtierende Präsident knowledge welche der folgenden Personen...
                AK26024 ) #knowledge welche der folgenden Personen..

#Recode the I don't knows 
gip_nov$AK26001[gip_nov$AK26001 < 0] <- NA

gip_nov$expAK26001_1 <- as.factor(gip_nov$expAK26001_1)

gip_nov <- gip_nov %>%
  mutate(experiment_groups_nov = recode(expAK26001_1, 
                                    "1" = "Control",                          
                                    "2" = "GFCC_Approves",
                                    "3" = "GFCC_Disapproves",
                                    "4" = "Kultusminister_Approves",
                                    "5" = "Kultusminister_Disapproves"
  )
  )


gip_nov$AK26001 %<>% as.factor() 

gip_nov <- gip_nov %>%
  mutate(sup_factor_nov = recode(AK26001, 
                             "1" = "disagree",                                
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

#check coding
table(gip_nov$sup_factor_nov, gip_nov$AK26001, useNA = "ifany")


```



```{r}


library(MASS)

m_gip_nov <- polr(sup_factor_nov ~ experiment_groups_nov, 
                  method = "probit",
                   data = gip_nov, 
                   Hess=TRUE)

summary(m_gip_nov)

#pvalues

(ctable <- coef(summary(m_gip_nov)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))



```


Make table for the Appendix:

```{r}
library(stargazer)

stargazer(m_gip_nov, 
          style = "ajps",
          type = "latex",
          title            = "Results of Ordinal Probit Regression Using GIP Wave 26, November 2016",
          covariate.labels = c("GFCC Approves", "GFCC Disapproves", "Minister of Education Approves", "Minister of Education Disapproves",
                               names(m_gip_nov$zeta)),
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Only data from the GIP Wave 26 from November 2016 is used for estimation."
)


```



## GIP Wave 27, January 2017

Prepare the data. 

```{r}

gip_jan <- read_dta("../Data/GIP_W27_V1.dta")

#subset only the necessary variables for experiment


gip_jan <- gip_jan %>%
  dplyr::select(id_g, expAK27030, #experimental groups
                AK27030, #response experioment
                AK27031, #trust_bverfg
                AK27034, #trust_government
                AK27035 ) #trust_judiciary



table(gip_jan$expAK27030, useNA = "ifany") #why are there NAs in the experimental setup?
table(gip_jan$AK27030, useNA = "ifany") #-99 and -90 are do not know.

table(gip_jan$AK27031, useNA = "ifany") #-99 and -90 are do not know.


#Recode the I don't knows to 
gip_jan$AK27030[gip_jan$AK27030 < 0] <- NA

table(gip_jan$AK27030, useNA = "ifany") #check

#recode NAs in trust gfcc:
gip_jan$AK27031[gip_jan$AK27031 < 0] <- NA

table(gip_jan$AK27031, useNA = "ifany") #check

#trust government:

gip_jan$AK27034[gip_jan$AK27034 < 0] <- NA

table(gip_jan$AK27034, useNA = "ifany") #check



#recode experimental groups:

gip_jan$expAK27030 <- as.factor(gip_jan$expAK27030)

gip_jan <- gip_jan %>%
  mutate(experiment_groups_jan = recode(expAK27030, 
                                    "1" = "Control",                                       
                                    "2" = "GFCC_Approves",
                                    "3" = "GFCC_Disapproves",
                                    "4" = "DPA_Approves",
                                    "5" = "DPA_Disapproves"
  )
  )


#recode outcome variable

gip_jan$AK27030 %<>% as.factor() 

gip_jan <- gip_jan %>%
  mutate(sup_factor_jan = recode(AK27030, 
                             "1" = "disagree",                                  
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

table(gip_jan$sup_factor_jan, gip_jan$AK27030, useNA = "ifany")

```


Run ordered probit only using the GIP January Wave 27 data:

```{r}


library(MASS)

m_gip_jan <- polr(sup_factor_jan ~ experiment_groups_jan, 
                   data = gip_jan, 
                   Hess=TRUE,
                  method = "probit")

summary(m_gip_jan)

#pvalues

(ctable <- coef(summary(m_gip_jan)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))



```

Make regression table for Appendix:

```{r}

library(stargazer)

stargazer(m_gip_jan, 
          style = "ajps",
          type = "latex",
          title            = "Results of Ordinal Probit Regression Using GIP Wave 27, January 2017",
          covariate.labels = c("GFCC Approves", "GFCC Disapproves", "Minister of Education Approves", "Minister of Education Disapproves",
                               names(m_gip_jan$zeta)),
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Only data from the GIP Wave 27 from January 2017 is used for estimation."
)


```

Pooled analysis:


```{r}

load("../Data/gip_merge.Rda")

gip_merge$experiment_groups_jan <- as.character(gip_merge$experiment_groups_jan)
gip_merge$experiment_groups_nov <- as.character(gip_merge$experiment_groups_nov)

```


```{r}

gip_wave<- c(rep("Januar", length(gip_merge$experiment_groups_jan)), rep("November", length(gip_merge$experiment_groups_nov)))


```



```{r}

#create outcome vector

response_vector <- c(gip_merge$sup_factor_nov, gip_merge$sup_factor_jan)

#back to factor
response_vector <- as.factor(response_vector)

#create experimental group vector

experiment_gr <- c(gip_merge$experiment_groups_nov, gip_merge$experiment_groups_jan)
  
#as factor as well  
experiment_gr <- as.factor(experiment_gr)

#ids for clustered SEs:

ids_gip <- as.factor(c(gip_merge$id_g, gip_merge$id_g))

#create new data set:

gip_analysis <- cbind.data.frame(ids_gip, experiment_gr, response_vector, gip_wave)

#omit NAs for clustered SE estimation

gip_analysis <- na.omit(gip_analysis) #get rid of NAs. These are the respondents who refused to answer or did not answer


#recode outcome :

gip_analysis <- gip_analysis %>%
  mutate(response_vector = recode(response_vector, 
                             "1" = "disagree",                                
                             "2" = "indifferent",
                             "3" = "agree"
  )
  ) 

#check order: important for later that the direction of the regression is in line with the order of the factor:

levels(gip_analysis$response_vector) #check


#estimate ordered probit:

m_pooled <- polr(response_vector ~ experiment_gr + gip_wave,
                    data = gip_analysis,
                    method = "probit",
                   Hess=TRUE)

summary(m_pooled)

#pvalues

(ctable <- coef(summary(m_pooled)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))


#estimate clustered SEs:

library(lmtest)
library(sandwich)

ses_m_gip_basic <- coeftest(m_pooled, vcov=vcovCL(m_pooled, factor(gip_analysis$ids_gip) ))

```


## Knowledge Interaction

-99 is "don't know", thus not coded as missing. Only -90 coded as missing. The knowledge questions are exactly coded as in the DCE paper. 

```{r}
#recode NAs
gip_merge$AK26023[gip_merge$AK26023 == -90] <- NA
gip_merge$AK26024[gip_merge$AK26024 == -90] <- NA

gip_merge$AK26023[gip_merge$AK26023 == -99] <- NA
gip_merge$AK26024[gip_merge$AK26024 == -99] <- NA

#check
table(gip_merge$AK26023, useNA = "ifany")
table(gip_merge$AK26024, useNA = "ifany")

gip_merge$know_voss <- gip_merge$AK26023
gip_merge$know_baer <- gip_merge$AK26024

```

For know_voss, category 2 is the correct answer. For know_baer, category 3 is the correct answer. 

```{r}

k1 <- ifelse(gip_merge$know_voss == 2, 1, 0)
k2 <- ifelse(gip_merge$know_baer == 3, 1, 0)

know <- k1 + k2

prop.table(table(k1,k2))

prop.table(table(know, useNA = "ifany"))
prop.table(table(know))

#recode into dummy

know_dummy <- ifelse(know == 0, 0, 1)
know_dummy[is.na(know_dummy)] <- 0

table(know_dummy, know)
prop.table(table(know_dummy, useNA = "ifany"))

```

Around 41 % could at least answer one of the two questions. These are the experts.


```{r}
gip_merge$know_dummy <- know_dummy

merge_knowledge <- data.frame(ids_gip = as.character(gip_merge$id_g), know_dummy = gip_merge$know_dummy)

gip_analysis <- left_join(gip_analysis, merge_knowledge)

#run analysis again, first for supsamples. 


m_gip_knowledge <- polr(response_vector ~ experiment_gr*know_dummy, 
                   data = gip_analysis, 
                   Hess=TRUE)

summary(m_gip_knowledge)

#pvalues

(ctable <- coef(summary(m_gip_knowledge)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table

(ctable <- cbind(ctable, "p value" = round(p, 4)))


#stargazer it:

stargazer(m_gip_knowledge, 
          style = "ajps",
          type = "latex",
          title            = "Results of Ordinal Probit Regression for Knowledge Interaction",
          covariate.labels = c("GFCC Approves", "GFCC Disapproves", "Minister of Education Approves", "Minister of Education Disapproves",
                               names(m_gip_knowledge$zeta)),
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Standard errors clustered by respondent."
)




````


## Original 5 point scale:


```{r}

gip_nov <- read_dta("../Data/GIP_W26_V2.dta")

#subset only the necessary variables for experiment

gip_nov <- gip_nov %>%
  dplyr::select(id_g, 
                expAK26001_1, #experimental groups
                AK26001, #outcome experiment
                AK26023, # amtierende Präsident nowledge welche der folgenden Personen...
                AK26024 ) #knowledge welche der folgenden Personen..



table(gip_nov$expAK26001_1, useNA = "ifany") #why are there NAs in the experimental setup?
table(gip_nov$AK26001, useNA = "ifany") #-99 and -90 are do not know.


#Recode the I don't knows to 
gip_nov$AK26001[gip_nov$AK26001 < 0] <- NA


table(gip_nov$AK26001, useNA = "ifany") #check




gip_nov$expAK26001_1 <- as.factor(gip_nov$expAK26001_1)

gip_nov <- gip_nov %>%
  mutate(experiment_groups_nov = recode(expAK26001_1, 
                                    "1" = "Control",                                       
                                    "2" = "GFCC_Approves",
                                    "3" = "GFCC_Disapproves",
                                    "4" = "Kultusminister_Approves",
                                    "5" = "Kultusminister_Disapproves"
  )
  )

###
gip_jan <- read_dta("../Data/GIP_W27_V1.dta")


#subset only the necessary variables for experiment


gip_jan <- gip_jan %>%
  dplyr::select(id_g, expAK27030, #experimental groups
                AK27030, #response experioment
                AK27031, #trust_bverfg
                AK27034, #trust_government
                AK27035 ) #trust_judiciary



table(gip_jan$expAK27030, useNA = "ifany") #why are there NAs in the experimental setup?
table(gip_jan$AK27030, useNA = "ifany") #-99 and -90 are do not know.

table(gip_jan$AK27031, useNA = "ifany") #-99 and -90 are do not know.


#Recode the I don't knows to 
gip_jan$AK27030[gip_jan$AK27030 < 0] <- NA

table(gip_jan$AK27030, useNA = "ifany") #check

#recode NAs in trust gfcc:
gip_jan$AK27031[gip_jan$AK27031 < 0] <- NA

table(gip_jan$AK27031, useNA = "ifany") #check

#trust government:

gip_jan$AK27034[gip_jan$AK27034 < 0] <- NA

table(gip_jan$AK27034, useNA = "ifany") #check



#recode experimental groups:

gip_jan$expAK27030 <- as.factor(gip_jan$expAK27030)

gip_jan <- gip_jan %>%
  mutate(experiment_groups_jan = recode(expAK27030, 
                                    "1" = "Control",                                       
                                    "2" = "GFCC_Approves",
                                    "3" = "GFCC_Disapproves",
                                    "4" = "DPA_Approves",
                                    "5" = "DPA_Disapproves"
  )
  )

###

gip_merge <-  left_join(gip_jan, gip_nov)

gip_merge$experiment_groups_jan <- as.character(gip_merge$experiment_groups_jan)
gip_merge$experiment_groups_nov <- as.character(gip_merge$experiment_groups_nov)

#create outcome vector

response_vector <- c(gip_merge$AK26001, gip_merge$AK27030)

#back to factor
response_vector <- as.factor(response_vector)

#create experimental group vector

experiment_gr <- c(gip_merge$experiment_groups_nov, gip_merge$experiment_groups_jan)
  
#as factor as well  
experiment_gr <- as.factor(experiment_gr)

#ids for clustered SEs:

ids_gip <- as.factor(c(gip_merge$id_g, gip_merge$id_g))

#create new data set:

gip_analysis <- cbind.data.frame(ids_gip, experiment_gr, response_vector)

#omit NAs for clustered SE estimation

gip_analysis <- na.omit(gip_analysis) #get rid of NAs. These are the respondents who refused to answer or did not answer


gip_analysis <- gip_analysis %>%
  mutate(response_vector = recode(response_vector, 
                                    "1" = "fullydis",                                       
                                    "2" = "dis",
                                    "3" = "indifferent",
                                    "4" = "ag",
                                    "5" = "fully_ag"
  )
  )


```


Run the model:

```{r}

m_gip_5point <- polr(response_vector ~ experiment_gr, 
                  method = "probit",
                   data = gip_analysis, 
                   Hess=TRUE)

summary(m_gip_5point)

#pvalues

(ctable <- coef(summary(m_gip_5point)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = round(p, 4)))


library(lmtest)
library(sandwich)

ses_m_gip_5point <- coeftest(m_gip_5point, vcov=vcovCL(m_gip_5point, factor(gip_analysis$ids_gip) ))


#Make Table:

library(stargazer)

stargazer(m_gip_5point, 
          style = "ajps",
          type = "latex",
                    coef = list(summary(m_gip_5point)$coefficients[,1]),
           se = list(ses_m_gip_5point[,2]),
          #t = ses_m_gip_basic[,3],
          p = list(ses_m_gip_5point[, 4]),
          title            = "Results of Ordinal Probit Regression Using GIP Wave 26, November 2016",
          covariate.labels = c("Data Security Official Approves", "Data Security Official Disapproves",
            "GFCC Approves", "GFCC Disapproves", "Minister of Education Approves", "Minister of Education Disapproves",
                               names(m_gip_5point$zeta)),
          column.labels = "test",
          dep.var.caption  = "DV: 3-Scale Rating of Likeability School Security Law",
          ord.intercepts = T,
          notes = "All included variables are dummies for the treatement group. The baseline category is the control group (no treatement). Only data from the GIP Wave 26 from November 2016 is used for estimation."
)


```


## Robustness trust rating independent of the treatment group. 

```{r}
merge_trustdf <- data.frame(ids_gip = as.factor(gip_merge$id_g), trust_gfcc = as.numeric(gip_merge$AK27031))

gip_analysis <- left_join(gip_analysis,merge_trustdf)

```


```{r}

t.test(gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "Control"], gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Approves"])

t.test(gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "Control"], gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Disapproves"])

t.test(gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Approves"], gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Disapproves"])

```

Both are not significant. Therefore, the respondent's trust rating is not influenced by the experimental manipulation.

## Robustness trust rating independent of the treatment group. 

```{r}


t.test(gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "Control"], gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Approves"])

t.test(gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "Control"], gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Disapproves"])

t.test(gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Approves"], gip_analysis$trust_gfcc[gip_analysis$experiment_gr == "GFCC_Disapproves"])

```

Both are not significant. Therefore, the respondent's trust rating is not influenced by the experimental manipulation.



## Robustness Check Different Policy Issue ENEF, France

Data Prep:

```{r}

df <- read_dta("../Data/ENEF2017_legitimacy_experiment.dta")

#Recode experimental groups:

class(df$ID12)
class(df$QEXPPOSINS)


df$PEXPPOSINS <- as.factor(df$PEXPPOSINS)

#recode the education variable

df <- df %>%
  mutate(experiment_groups_school = recode(PEXPPOSINS, 
                                    "1" = "Control",                                       
                                    "2" = "CC_Approves",
                                    "3" = "CC_Disapproves",
                                    "4" = "Haut_Conseil_Edu_Approves",
                                    "5" = "Haut_Conseil_Edu_Disapproves"
  )
  )


df$QEXPPOSINS <- as.factor(df$QEXPPOSINS)

#recode the pension variable
df <- df %>%
  mutate(experiment_groups_pension = recode(QEXPPOSINS, 
                                    "1" = "Control",                                       
                                    "2" = "CC_Approves",
                                    "3" = "CC_Disapproves",
                                    "4" = "Conseil_d_Orientation_appr.",
                                    "5" = "Conseil_d_Orientation_disappr."
  )
  )


#recode NAs
df$PCCFAITH[df$PCCFAITH > 6] <- NA
df$QCCFAITH[df$QCCFAITH > 6] <- NA

table(df$PCCFAITH, useNA = "ifany")
table(df$QCCFAITH, useNA = "ifany")


#short check:

#first reverse to have the German coding:

df$PCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_school  = recode(PCCFAITH, 
                             "1" = "5",                                  
                             "2" = "4",
                             "3" = "3",
                             "4" = "2",
                             "5" = "1"
  )
  ) 
#order levels again

df$rating_school <- factor(df$rating_school, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_school, df$PCCFAITH)


###do the same for the pension variable

df$QCCFAITH %<>% as.factor() 

df <- df %>%
  mutate(rating_pension  = recode(QCCFAITH, 
                             "1" = "5",                                  
                             "2" = "4",
                             "3" = "3",
                             "4" = "2",
                             "5" = "1"
  )
  ) 
#order levels again

df$rating_pension <- factor(df$rating_pension, levels = c("1", "2", "3", "4", "5"))
#check:
table(df$rating_pension, df$QCCFAITH)


#################
#continue recoding: now to 3-point scale

df <- df %>%
  mutate(rating_school_factor = recode(rating_school, 
                             "1" = "disagree",                                  
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_school, df$rating_school_factor, useNA = "ifany")


#same for pension policy experiment

df <- df %>%
  mutate(rating_pension_factor = recode(rating_pension, 
                             "1" = "disagree",                                  
                             "2" = "disagree",
                             "3" = "indifferent",
                             "4" = "agree",
                             "5" = "agree"
  )
  ) 

#check recoding:
table(df$rating_pension, df$rating_pension_factor, useNA = "ifany")




```

